---
title: "pt2"
author: "Xuan Nguyen"
date: "2024-11-12"
output:
  pdf_document: default
  html_document: default
---


# Load necessary libraries
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
```


  
```
# Load the data (replace with your file path)
```{r}
data <- read.csv("/Users/xuanmn/Desktop/CSS 451/final project/pt2/API_EN.GHG.ALL.MT.CE.AR5_DS2_en_csv_v2_10763.csv", skip = 4)
```

# Filter for the countries of interest and select the relevant columns
```{r}
print(colnames(data)) 
years <- paste0("X", 2015:2022)  
countries_of_interest <- c("United States", "China", "Russian Federation", "Brazil", "United Kingdom")
```

# Filter and select columns
```{r}
selected_data <- data %>%
  filter(Country.Name %in% countries_of_interest) %>%
  select(Country.Name, all_of(years))
colnames(selected_data) <- gsub("^X", "", colnames(selected_data))
```
# Plotted data
```{r}
selected_data_long <- selected_data %>%
  pivot_longer(cols = -Country.Name, names_to = "Year", values_to = "Emissions") %>%
  mutate(Year = as.integer(Year)) # Convert Year to integer for proper plotting
  
  ggplot(selected_data_long, aes(x = Year, y = Emissions, color = Country.Name)) +
  geom_line(size = 1) +
  geom_point() +
  labs(title = "Greenhouse Gas Emissions (2015-2022)",
       x = "Year",
       y = "Emissions (Million metric tons of CO2 equivalent)",
       color = "Country") +
  theme_minimal()
```


